Manuscript results: Forecasting influenza using ARIMA and ARIMAX

### 2025-05-06 manuscript_results.Rmd
update

# Plotting forecasts and ribbon
plt00 <- ggplot(forecast_df, aes(x = Week, y = Value, group = 1)) +
  geom_line(color = "black", size = 1) +          # Line connecting forecast values
  geom_point(color = "black", size = 3) +         # Points for each forecast value
  geom_ribbon(aes(ymin = Lower, ymax = Upper),   # Ribbon for confidence intervals
              fill = "gray", alpha = 0.25) +
  labs(title = "Figure X: Example of influenza hospitalizaions forecasts",
       subtitle = "The gray ribbon indicates the 95% confidence interval",
       x = "Target Weeks",
       y = "Forecast Values") +
  theme_minimal() +
  theme(plot.title = element_text(size = 16, face = "bold"),
        plot.subtitle = element_text(size = 14))

@@

ggsave(plt00, height = 5, width = 10, filename="fig00.jpg") 
```

@@

# Plot
plt0 <- ggplot(df_combined_, aes(x = Julian_date, y = WIS, group = STATE)) + 
  geom_vline(data = highlight_dates, aes(xintercept = Julian_date), color = "red", linetype = "dashed", size = 1) +  
  geom_line(color = "black", size = 0.2) +  
  facet_wrap(~ Dataset, ncol = 2, scales = "free_y") +  
  theme_minimal() +  
  labs(title = "Figure X: Baseline model WIS for 48 states on the contiguous U.S.",#,
#       subtitle = "Dashed red lines indicates epidemiological weeks outsise of the influenza season",
       x = "Month", 
       y = "WIS") +  
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        plot.title = element_text(size = 16, face = "bold"),
        legend.position = "none") + 
  scale_x_date(labels = scales::date_format("%b"), breaks = "2 month")  # Format x-axis to show months and set monthly breaks

@@

ggsave(plt0, height = 5, width = 8, filename="fig0.jpg")  
```

@@

# Combine in a 2x2 grid
combined_plot <- (plt1 | plt2) + 
  plot_annotation(
    title = "Figure X: Mean WIS for our 24 models",
    subtitle = "Results by forecast horizon",
    theme = theme(plot.title = element_text(size = 16, face = "bold"),
                  plot.subtitle = element_text(size = 14))
  )
# Print
print(combined_plot)

# Save to file
ggsave("Fig1.jpg", combined_plot, width =13, height =7)
```

@@

# Create the plot
combined_plot <- ggplot(all_weeks, aes(x = Best_Result, fill = Best_Result)) +
  geom_bar() +
  scale_fill_manual(values = custom_colors) +
  labs(title = "Figure X: Best model based on the lowest mean WIS",
       subtitle = "Across the 48 states on the contiguous U.S.",
       x = "", y = "Number of states",
       fill = "Best model" ) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        plot.title = element_text(size = 16, face = "bold")) +
  facet_grid(Week_Ahead ~ Model_Type, scales = "free_x")

# Save and display the plot
ggsave("Fig2.jpg", combined_plot, width =8, height =5)
print(combined_plot)

@@

# Heatmap plot with models ordered by WeekAhead == 1  
plot_m_heatmap <- ggplot(p_df, aes(x = factor(WeekAhead), y = Model, fill = m)) +
  geom_tile(aes(fill = ifelse(Significance == "Significant", m, NA)), color = "black") +  # Fill only significant ones
  geom_tile(data = p_df %>% filter(Significance == "Not Significant"), 
            aes(x = factor(WeekAhead), y = Model), fill = "gray80", color = "black") +  # Gray for non-significant
  geom_text(aes(label = paste0("m:", round(m, 1),", sd:", round(sd, 1))), 
            color = "black", size = 4) +  # Add text labels
  scale_fill_gradient(low = "cyan", high = "red", na.value = "gray80", 
                      name = "Percentage (%)", limits = c(-35, 35)) +  # Fixed color scale from -30 to 30
  labs(title = "Figure X: Mean differences between models' WIS and the baseline across 48 states",
       subtitle = "Gray boxes indicate models that are not significantly different from the baseline (p>0.05)",
         caption = "m = mean difference (%), sd = standard deviation",
       x = "Week Ahead",
       y = "") + 
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
  plot.caption = element_text(size = 16),
    plot.title = element_text(size = 18, face = "bold"),
    plot.subtitle = element_text(size = 14),) +
  facet_wrap(~ Model_Type, scales = "free_y")  # Separate NoLg and other models

# Print plot
print(plot_m_heatmap)
ggsave("Fig3.jpg", plot_m_heatmap, width = 14, height = 7 )

@@

ES_1WEEK <- ggplot(W1_map) +
  geom_sf(aes(fill = AUTO_AVG)) +  # Fill based on the best model
  scale_fill_gradient2(low = "skyblue", mid = "lightyellow2", high = "red", midpoint = 100, limits = c(0, 352)) +  
  ggtitle("1 Week Ahead") +
  theme_light() +
  theme(legend.position = "right",
    plot.title = element_text(hjust = 0.5)) +
  geom_sf_text(data = W1_map, aes(label = round(AUTO_AVG,0)),  # Round to whole numbers
               size = 3,
               color = "black",
               check_overlap = TRUE,fontface = "bold") +  # Display percentage improvement in each state
  labs(
    fill = "mean WIS",  
       x = "",
       y = ""
  )  # Adding a subtitle

@@

ES_2WEEK <- ggplot(W2_map) +
  geom_sf(aes(fill = AUTO_AVG)) +  # Fill based on the best model
  scale_fill_gradient2(low = "skyblue", mid = "lightyellow2", high = "red", midpoint = 100, limits = c(0, 352)) +  
  ggtitle("2 Weeks Ahead") +
  theme_light() +
  theme(legend.position = "right",
    plot.title = element_text(hjust = 0.5)) +
  geom_sf_text(data = W2_map, aes(label = round(AUTO_AVG,0)),  # Round to whole numbers
               size = 3,
               color = "black",
               check_overlap = TRUE,fontface = "bold") +  # Display percentage improvement in each state
  labs(
    fill = "mean WIS",
       x = "",
       y = ""
  )  # Adding a subtitle

@@

ES_3WEEK <- ggplot(W3_map) +
  geom_sf(aes(fill = AUTO_AVG)) +  # Fill based on the best model
  scale_fill_gradient2(low = "skyblue", mid = "lightyellow2", high = "red", midpoint = 100, limits = c(0, 352)) +  
  ggtitle("3 Weeks Ahead") +
  theme_light() +
  theme(legend.position = "right",
    plot.title = element_text(hjust = 0.5)) +
  geom_sf_text(data = W3_map, aes(label = round(AUTO_AVG,0)),  # Round to whole numbers
               size = 3,
               color = "black",
               check_overlap = TRUE,fontface = "bold") +  # Display percentage improvement in each state
  labs(
    fill = "mean WIS",
       x = "",
       y = ""
  )  # Adding a subtitle

@@

ES_4WEEK <- ggplot(W4_map) +
  geom_sf(aes(fill = AUTO_AVG)) +
  scale_fill_gradient2(low = "skyblue", mid = "lightyellow2", high = "red", 
                       midpoint = 100, limits = c(0, 352)) +  
  ggtitle("4 Weeks Ahead") +
  theme_light() +
  theme(legend.position = "right",
    plot.title = element_text(hjust = 0.5)) +
  geom_sf_text(data = W4_map, aes(label = round(AUTO_AVG,0)),  
               size = 3,
               color = "black",
               check_overlap = TRUE,fontface = "bold") +
  labs(
    fill = "mean WIS", 
       x = "",
       y = ""
  )

@@

```{r}
# Combine in a 2x2 grid
combined_plot <- (ES_1WEEK | ES_2WEEK) /
                 (ES_3WEEK | ES_4WEEK) + 
  plot_annotation(
    title = "Figure X: Mean WIS for the 48 states in the contiguous U.S.",
    subtitle = "Results for the the 2022/2023 and 2023/2024 influenza seasons",
    theme = theme(plot.title = element_text(size = 16, face = "bold"),
                  plot.subtitle = element_text(size = 14))
  )
# Print
print(combined_plot)

# Save to file
ggsave("Fig4.jpg", combined_plot, width =12, height =7)

@@

# Plot
reg2<-ggplot(regression_models, aes(x = Week_Ahead, y = independent_variable, fill = significance)) +  
  geom_tile(color = "black") +  # Add black borders to squares
  geom_text(aes(label = round(r_squared, 3)), color = "black", size = 6) +  # Text inside boxes
  scale_fill_manual(values = c("Significant" = "cyan", "Not Significant" = "gray")) +  
  labs(title = "Regression models",
       subtitle = "Mean WIS as dependent variable",
       x = "Week Ahead",
       y = "Independent Variables",
       fill = "Significance (p < 0.05)") +  
  theme_minimal() +  
  theme(axis.text.x = element_text(angle = 45, hjust = 1), 
        axis.text.y = element_text(size = 10))

@@

ggsave(reg2, height = 8, width = 10, filename="Fig4E.jpg")  
#ggsave(reg2, filename="reg2.jpg",height = 8, width = 10)
```

@@

ES_1WEEK <- ggplot(W1_map) +
  geom_sf(aes(fill = percentage_improvement)) +  # Fill based on the best model
  scale_fill_gradient2(low ="skyblue" , mid = "lightyellow", high = "darkred", midpoint = 0, limits = c(-60, 30)) +  
  ggtitle("1 Week Ahead") +
  theme_light() +
  theme(legend.position = "right",
    plot.title = element_text(hjust = 0.5)) +
  geom_sf_text(data = W1_map, aes(label = round(percentage_improvement,0)),  # Round to whole numbers
               size = 3,
               color = "black",
               check_overlap = TRUE,fontface = "bold") +  # Display percentage improvement in each state
  labs(
    fill = "Percentage (%)",  # Label for the legend
       x = "",
       y = ""
  )  # Adding a subtitle

@@

ES_2WEEK <- ggplot(W2_map) +
  geom_sf(aes(fill = percentage_improvement)) +  # Fill based on the best model
  scale_fill_gradient2(low ="skyblue" , mid = "lightyellow", high = "darkred", midpoint = 0, limits = c(-60, 30)) +  
  ggtitle("2 Weeks Ahead") +
  theme_light() +
  theme(legend.position = "right",
    plot.title = element_text(hjust = 0.5)) +
  geom_sf_text(data = W2_map, aes(label = round(percentage_improvement,0)),  # Round to whole numbers
               size = 3,
               color = "black",
               check_overlap = TRUE,fontface = "bold") +  # Display percentage improvement in each state
  labs(
    fill = "Percentage (%)",  # Label for the legend
       x = "",
       y = ""
  )  # Adding a subtitle

@@

ES_3WEEK <- ggplot(W3_map) +
  geom_sf(aes(fill = percentage_improvement)) +  # Fill based on the best model
  scale_fill_gradient2(low ="skyblue" , mid = "lightyellow", high = "darkred", midpoint = 0, limits = c(-60, 30)) +  
  ggtitle("3 Weeks Ahead") +
  theme_light() +
  theme(legend.position = "right",
    plot.title = element_text(hjust = 0.5)) +
  geom_sf_text(data = W3_map, aes(label = round(percentage_improvement,0)),  # Round to whole numbers
               size = 3,
               color = "black",
               check_overlap = TRUE,fontface = "bold") +  # Display percentage improvement in each state
  labs(
    fill =  "Percentage (%)",  # Label for the legend
       x = "",
       y = ""
  )  # Adding a subtitle

@@

```{r}
ES_4WEEK <- ggplot(W4_map) +
  geom_sf(aes(fill = percentage_improvement)) +  # Fill based on the best model
  scale_fill_gradient2(low ="skyblue" , mid = "lightyellow", high = "darkred", midpoint = 0, limits = c(-60, 30)) +  
  ggtitle("4 Weeks Ahead") +
  theme_light() +
  theme(legend.position = "right",
    plot.title = element_text(hjust = 0.5)) +
  geom_sf_text(data = W4_map, aes(label = round(percentage_improvement,0)),  # Round to whole numbers
               size = 3,
               color = "black",
               check_overlap = TRUE,fontface = "bold") +  # Display percentage improvement in each state
  labs(
    fill = "Percentage (%)",  # Label for the legend
       x = "",
       y = ""
  )  # Adding a subtitle

@@

# Combine in a 2x2 grid
combined_plot <- (ES_1WEEK | ES_2WEEK) /
                 (ES_3WEEK | ES_4WEEK) + 
  plot_annotation(
    title = "Figure X: Mean WIS differences (%) compared to the baseline",
    subtitle = "Results by forecast horizon",
    theme = theme(plot.title = element_text(size = 16, face = "bold"),
                  plot.subtitle = element_text(size = 14))
  )
# Print
print(combined_plot)

# Save to file
ggsave("Fig5.jpg", combined_plot, width =12, height =7)
```

@@

# Plot
reg2<-ggplot(regression_models, aes(x = Week_Ahead, y = independent_variable, fill = significance)) +  
  geom_tile(color = "black") +  # Add black borders to squares
  geom_text(aes(label = round(r_squared, 3)), color = "black", size = 6) +  # Text inside boxes
  scale_fill_manual(values = c("Significant" = "cyan", "Not Significant" = "gray")) +  
  labs(title = "Regression models",
       subtitle = "Percentage of WIS improvement as dependent variable",
       x = "Week Ahead",
       y = "Independent Variables",
       fill = "Significance (p < 0.05)") +    
  theme_minimal() +  
  theme(axis.text.x = element_text(angle = 45, hjust = 1), 
        axis.text.y = element_text(size = 10))

reg2
ggsave(reg2, filename="Fig5E.jpg",height = 8, width = 10)
```

@@

@@

# Plot the difference using ggplot2
model_improv<-ggplot(summed_data_all, aes(x = Julian_date, y = (Difference), color = Week)) +
  geom_point(size = 3) +
  geom_hline(yintercept = 0, color = "black", linetype = "dashed", size = 0.8) +
  theme_minimal() +
  labs(
    title = "Figure X: Mean percentage of WIS differences across all states",
    subtitle = "AUTO_AVG_LB compared to baseline",
    x = "",
    y = "Difference (%)"
  ) +
  scale_y_continuous(
    limits = c(-100, 100),
    breaks = seq(-100, 100, by = 20)
  ) +
  scale_x_date(
    date_breaks = "1 month",
    date_labels = "%b %y"
  ) +
  scale_color_manual(
    values = c("Week 1" = "#ffcccc",
               "Week 2" = "#ff6666",
               "Week 3" = "#cc0000",
               "Week 4" = "#990000")
  ) +
  theme(
    plot.title = element_text(size = 18, face = "bold"),
    plot.subtitle = element_text(size = 14),
    axis.text.x = element_text(angle = 45, hjust = 1)
  )

@@

ggsave(model_improv, height = 4.5, width = 9,  filename="Fig6.jpg")  
```

>>>>

# Plotting forecasts and ribbon
plt00 <- ggplot(forecast_df, aes(x = Week, y = Value, group = 1)) +
  geom_line(color = "black", size = 1) +          # Line connecting forecast values
  geom_point(color = "black", size = 3) +         # Points for each forecast value
  geom_ribbon(aes(ymin = Lower, ymax = Upper),   # Ribbon for confidence intervals
              fill = "gray", alpha = 0.25) +
  labs(title = "Figure 1: Example of probabilistic forecasts",
       subtitle = "The gray ribbon indicates the 95% confidence interval",
       x = "Target Weeks",
       y = "Forecast Values") +
  theme_minimal() +
  theme(plot.title = element_text(size = 16, face = "bold"),
        plot.subtitle = element_text(size = 14))

@@

ggsave(plt00, height = 4, width =7, filename="Fig1.jpg") 
```

@@

# Plot
plt0 <- ggplot(df_combined_, aes(x = Julian_date, y = WIS, group = STATE)) + 
  geom_vline(data = highlight_dates, aes(xintercept = Julian_date), color = "red", linetype = "dashed", size = 1) +  
  geom_line(color = "black", size = 0.1) +  
  facet_wrap(~ Dataset, ncol = 2, scales = "free_y") +  
  theme_minimal() +  
  labs(title = "Figure 2: Baseline model WIS for 48 states on the contiguous U.S.",#,
       subtitle = "Weeks between the dashed red lines are outside of the influenza season",
       x = "", 
       y = "WIS") +  
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        plot.title = element_text(size = 16, face = "bold"),
        legend.position = "none") +
  scale_x_date(
    date_breaks = "1 month",
    date_labels = "%b %y"
  ) # Format x-axis to show months and set monthly breaks

@@

ggsave(plt0, height = 5, width = 8, filename="Fig2.jpg")  
```

@@

# Combine in a 2x2 grid
combined_plot <- (plt1 | plt2) + 
  plot_annotation(
    title = "Figure 3: Mean WIS for our 24 models",
    subtitle = "Results by target week",
    theme = theme(plot.title = element_text(size = 16, face = "bold"),
                  plot.subtitle = element_text(size = 14))
  )
# Print
print(combined_plot)

# Save to file
ggsave("Fig3.jpg", combined_plot, width =13, height =7)
```

@@

# Create the plot
combined_plot <- ggplot(all_weeks, aes(x = Best_Result, fill = Best_Result)) +
  geom_bar() +
  scale_fill_manual(values = custom_colors) +
  labs(title = "Figure 4: Best model based on the lowest mean WIS",
       subtitle = "Results for the 48 states on the contiguous U.S. by target week",
       x = "", y = "Number of states",
       fill = "Best model" ) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        plot.title = element_text(size = 16, face = "bold")) +
  facet_grid(Week_Ahead ~ Model_Type, scales = "free_x")

# Save and display the plot
ggsave("Fig4.jpg", combined_plot, width =8, height =5)
print(combined_plot)

@@

# Heatmap plot with models ordered by WeekAhead == 1  
plot_m_heatmap <- ggplot(p_df, aes(x = factor(WeekAhead), y = Model, fill = m)) +
  geom_tile(aes(fill = ifelse(Significance == "Significant", m, NA)), color = "black") +  # Fill only significant ones
  geom_tile(data = p_df %>% filter(Significance == "Not Significant"), 
            aes(x = factor(WeekAhead), y = Model), fill = "gray80", color = "black") +  # Gray for non-significant
  geom_text(aes(label = paste0("m:", round(m, 1),", sd:", round(sd, 1))), 
            color = "black", size = 4) +  # Add text labels
  scale_fill_gradient(low = "cyan", high = "red", na.value = "gray80", 
                      name = "Percentage (%)", limits = c(-35, 35)) +  # Fixed color scale from -30 to 30
  labs(title = "Figure 5: Mean differences between models' WIS and the baseline across 48 states",
       subtitle = "Gray boxes indicate models that are not significantly different from the baseline (p>0.05)",
         caption = "m = mean difference (%), sd = standard deviation",
       x = "Target Ahead",
       y = "") + 
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
  plot.caption = element_text(size = 16),
    plot.title = element_text(size = 18, face = "bold"),
    plot.subtitle = element_text(size = 14),) +
  facet_wrap(~ Model_Type, scales = "free_y")  # Separate NoLg and other models

# Print plot
print(plot_m_heatmap)
ggsave("Fig5.jpg", plot_m_heatmap, width = 14, height = 7 )

@@

ES_1WEEK <- ggplot(W1_map) +
  geom_sf(aes(fill = AUTO_AVG)) +  # Fill based on the best model
  scale_fill_gradient2(low = "skyblue", mid = "lightyellow2", high = "red", midpoint = 100, limits = c(0, 352)) +  
  ggtitle("1 weeks ahead") +
  theme_light() +
  theme(legend.position = "right",
    plot.title = element_text(hjust = 0.5)) +
  geom_sf_text(data = W1_map, aes(label = round(AUTO_AVG,0)),  # Round to whole numbers
               size = 3,
               color = "black",
               check_overlap = TRUE,fontface = "bold") +  # Display percentage improvement in each state
  labs(
    fill = "mean WIS",  
       x = "",
       y = ""
  )  # Adding a subtitle

@@

ES_2WEEK <- ggplot(W2_map) +
  geom_sf(aes(fill = AUTO_AVG)) +  # Fill based on the best model
  scale_fill_gradient2(low = "skyblue", mid = "lightyellow2", high = "red", midpoint = 100, limits = c(0, 352)) +  
  ggtitle("2 weeks ahead") +
  theme_light() +
  theme(legend.position = "right",
    plot.title = element_text(hjust = 0.5)) +
  geom_sf_text(data = W2_map, aes(label = round(AUTO_AVG,0)),  # Round to whole numbers
               size = 3,
               color = "black",
               check_overlap = TRUE,fontface = "bold") +  # Display percentage improvement in each state
  labs(
    fill = "mean WIS",
       x = "",
       y = ""
  )  # Adding a subtitle

@@

ES_3WEEK <- ggplot(W3_map) +
  geom_sf(aes(fill = AUTO_AVG)) +  # Fill based on the best model
  scale_fill_gradient2(low = "skyblue", mid = "lightyellow2", high = "red", midpoint = 100, limits = c(0, 352)) +  
  ggtitle("3 weeks ahead") +
  theme_light() +
  theme(legend.position = "right",
    plot.title = element_text(hjust = 0.5)) +
  geom_sf_text(data = W3_map, aes(label = round(AUTO_AVG,0)),  # Round to whole numbers
               size = 3,
               color = "black",
               check_overlap = TRUE,fontface = "bold") +  # Display percentage improvement in each state
  labs(
    fill = "mean WIS",
       x = "",
       y = ""
  )  # Adding a subtitle

@@

ES_4WEEK <- ggplot(W4_map) +
  geom_sf(aes(fill = AUTO_AVG)) +
  scale_fill_gradient2(low = "skyblue", mid = "lightyellow2", high = "red", 
                       midpoint = 100, limits = c(0, 352)) +  
  ggtitle("4 weeks ahead") +
  theme_light() +
  theme(legend.position = "right",
    plot.title = element_text(hjust = 0.5)) +
  geom_sf_text(data = W4_map, aes(label = round(AUTO_AVG,0)),  
               size = 3,
               color = "black",
               check_overlap = TRUE,fontface = "bold") +
  labs(
    fill = "mean WIS", 
       x = "",
       y = ""
  )

@@

```{r}
# Combine in a 2x2 grid
combined_plot <- (ES_1WEEK | ES_2WEEK) /
                 (ES_3WEEK | ES_4WEEK) + 
  plot_annotation(
    title = "Figure 6: Mean WIS for the 48 states in the contiguous U.S.",
    subtitle = "Results for the the 2022/2023 and 2023/2024 influenza seasons",
    theme = theme(plot.title = element_text(size = 16, face = "bold"),
                  plot.subtitle = element_text(size = 14))
  )
# Print
print(combined_plot)

# Save to file
ggsave("Fig6.jpg", combined_plot, width =12, height =7)

@@

# Plot
reg2<-ggplot(regression_models, aes(x = Week_Ahead, y = independent_variable, fill = significance)) +  
  geom_tile(color = "black") +  # Add black borders to squares
  geom_text(aes(label = round(r_squared, 3)), color = "black", size = 6) +  # Text inside boxes
  scale_fill_manual(values = c("Significant" = "cyan", "Not Significant" = "gray")) +  
  labs(title = "Figure 7: Regression models",
       subtitle = "Mean WIS as dependent variable",
       x = "Week Ahead",
       y = "Independent Variables",
       fill = "Significance (p < 0.05)") +  
  theme_minimal() +  
  theme(axis.text.x = element_text(angle = 45, hjust = 1), 
        axis.text.y = element_text(size = 10),
        plot.title = element_text(size = 16, face = "bold"),
                  plot.subtitle = element_text(size = 14))

@@

ggsave(reg2, height = 6, width = 8, filename="Fig7.jpg")  
#ggsave(reg2, filename="reg2.jpg",height = 8, width = 10)
```

@@

ES_1WEEK <- ggplot(W1_map) +
  geom_sf(aes(fill = percentage_improvement)) +  # Fill based on the best model
  scale_fill_gradient2(low ="skyblue" , mid = "lightyellow", high = "darkred", midpoint = 0, limits = c(-60, 30)) +  
  ggtitle("1 weeks ahead") +
  theme_light() +
  theme(legend.position = "right",
    plot.title = element_text(hjust = 0.5)) +
  geom_sf_text(data = W1_map, aes(label = round(percentage_improvement,0)),  # Round to whole numbers
               size = 3,
               color = "black",
               check_overlap = TRUE,fontface = "bold") +  # Display percentage improvement in each state
  labs(
    fill = "Percentage (%)",  # Label for the legend
       x = "",
       y = ""
  )  # Adding a subtitle

@@

ES_2WEEK <- ggplot(W2_map) +
  geom_sf(aes(fill = percentage_improvement)) +  # Fill based on the best model
  scale_fill_gradient2(low ="skyblue" , mid = "lightyellow", high = "darkred", midpoint = 0, limits = c(-60, 30)) +  
  ggtitle("2 weeks ahead") +
  theme_light() +
  theme(legend.position = "right",
    plot.title = element_text(hjust = 0.5)) +
  geom_sf_text(data = W2_map, aes(label = round(percentage_improvement,0)),  # Round to whole numbers
               size = 3,
               color = "black",
               check_overlap = TRUE,fontface = "bold") +  # Display percentage improvement in each state
  labs(
    fill = "Percentage (%)",  # Label for the legend
       x = "",
       y = ""
  )  # Adding a subtitle

@@

ES_3WEEK <- ggplot(W3_map) +
  geom_sf(aes(fill = percentage_improvement)) +  # Fill based on the best model
  scale_fill_gradient2(low ="skyblue" , mid = "lightyellow", high = "darkred", midpoint = 0, limits = c(-60, 30)) +  
  ggtitle("3 weeks ahead") +
  theme_light() +
  theme(legend.position = "right",
    plot.title = element_text(hjust = 0.5)) +
  geom_sf_text(data = W3_map, aes(label = round(percentage_improvement,0)),  # Round to whole numbers
               size = 3,
               color = "black",
               check_overlap = TRUE,fontface = "bold") +  # Display percentage improvement in each state
  labs(
    fill =  "Percentage (%)",  # Label for the legend
       x = "",
       y = ""
  )  # Adding a subtitle

@@

```{r}
ES_4WEEK <- ggplot(W4_map) +
  geom_sf(aes(fill = percentage_improvement)) +  # Fill based on the best model
  scale_fill_gradient2(low ="skyblue" , mid = "lightyellow", high = "darkred", midpoint = 0, limits = c(-60, 30)) +  
  ggtitle("4 weeks ahead") +
  theme_light() +
  theme(legend.position = "right",
    plot.title = element_text(hjust = 0.5)) +
  geom_sf_text(data = W4_map, aes(label = round(percentage_improvement,0)),  # Round to whole numbers
               size = 3,
               color = "black",
               check_overlap = TRUE,fontface = "bold") +  # Display percentage improvement in each state
  labs(
    fill = "Percentage (%)",  # Label for the legend
       x = "",
       y = ""
  )  # Adding a subtitle

@@

# Combine in a 2x2 grid
combined_plot <- (ES_1WEEK | ES_2WEEK) /
                 (ES_3WEEK | ES_4WEEK) + 
  plot_annotation(
    title = "Figure 8: Mean WIS differences (%) compared to the baseline",
    subtitle = "Results by forecast horizon",
    theme = theme(plot.title = element_text(size = 16, face = "bold"),
                  plot.subtitle = element_text(size = 14))
  )
# Print
print(combined_plot)

# Save to file
ggsave("Fig8.jpg", combined_plot, width =12, height =7)
```

@@

# Plot
reg2<-ggplot(regression_models, aes(x = Week_Ahead, y = independent_variable, fill = significance)) +  
  geom_tile(color = "black") +  # Add black borders to squares
  geom_text(aes(label = round(r_squared, 3)), color = "black", size = 6) +  # Text inside boxes
  scale_fill_manual(values = c("Significant" = "cyan", "Not Significant" = "gray")) +  
  labs(title = "Figure 9: Regression models",
       subtitle = "Mean WIS differences (%) as dependent variable",
       x = "Target Ahead",
       y = "Independent Variables",
       fill = "Significance (p < 0.05)") +    
  theme_minimal() +  
  theme(axis.text.x = element_text(angle = 45, hjust = 1), 
        axis.text.y = element_text(size = 10),
        plot.title = element_text(size = 16, face = "bold"),
                  plot.subtitle = element_text(size = 14))

reg2
ggsave(reg2, filename="Fig9.jpg",height = 6, width = 8)
```

@@

```{r}
# Create a list of data frames for the four weeks
weeks <- 1:4
summed_data_list <- list()

@@

# Plot the difference using ggplot2
model_improv<-ggplot(summed_data_all, aes(x = Julian_date, y = (Difference), color = Week)) +
  geom_point(size = 3) +
  geom_hline(yintercept = 0, color = "black", linetype = "dashed", size = 0.8) +
  theme_minimal() +
  labs(
    title = "Figure 10: Mean percentage of WIS differences across all states",
    subtitle = "AUTO_AVG_LB compared to baseline",
    x = "",
    y = "Difference (%)"
  ) +
  scale_y_continuous(
    limits = c(-100, 100),
    breaks = seq(-100, 100, by = 20)
  ) +
  scale_x_date(
    date_breaks = "1 month",
    date_labels = "%b %y"
  ) +
  scale_color_manual(
    values = c("Week 1" = "#ffcccc",
               "Week 2" = "#ff6666",
               "Week 3" = "#cc0000",
               "Week 4" = "#990000")
  ) +
  theme(
    plot.title = element_text(size = 18, face = "bold"),
    plot.subtitle = element_text(size = 14),
    axis.text.x = element_text(angle = 45, hjust = 1)
  )

@@

ggsave(model_improv, height = 4.5, width = 9,  filename="Fig10.jpg")  
```
Talvez incluir standar deviation das diferenceas

  # Calculate the percentage difference at the row level (i.e., per state-date)
  data__ <- data__ %>%
    mutate(Difference = ((AUTO_AVG_LB / AUTO_AR) - 1) * 100)

  # Group by Julian date and calculate mean and standard deviation of Difference
  summarized <- data__ %>%
    group_by(Julian_date) %>%
    summarize(
      Mean_Diff = Difference,
      SD_Diff = sd(Difference, na.rm = TRUE)
    ) %>%
    mutate(Week = paste0("Week ", week))

  # Store the summarized data
  summed_data_list[[week]] <- summarized
}

# Plot the mean difference with error bars for standard deviation
model_improv <- ggplot(summed_data_all, aes(x = Julian_date, y = Mean_Diff, color = Week)) +
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = Mean_Diff - SD_Diff, ymax = Mean_Diff + SD_Diff), width = 0.5) +
  geom_hline(yintercept = 0, color = "black", linetype = "dashed", size = 0.8) +
  theme_minimal() +
  labs(
    title = "Figure 10: Mean percentage of WIS differences across all states",
    subtitle = "AUTO_AVG_LB compared to baseline",
    x = "",
    y = "Difference (%)"
  ) +
  scale_y_continuous(
    limits = c(-100, 100),
    breaks = seq(-100, 100, by = 20)
  ) +
  scale_x_date(
    date_breaks = "1 month",
    date_labels = "%b %y"
  ) +
  scale_color_manual(
    values = c("Week 1" = "#ffcccc",
               "Week 2" = "#ff6666",
               "Week 3" = "#cc0000",
               "Week 4" = "#990000")
  ) +
  theme(
    plot.title = element_text(size = 18, face = "bold"),
    plot.subtitle = element_text(size = 14),
    axis.text.x = element_text(angle = 45, hjust = 1)
  )

#ggsave(model_improv, height = 4.5, width = 9, filename = "Fig11.jpg")
